\problemname{Robot Riot}

A group of high school students have recently been experimenting with robots.
They had long feared this day would come, but now their worst nightmare has
been realized: the artificial intelligence of the robots has become so advanced
that they've started to think for themselves, and are of course going to
destroy all humanity.

Fortunately there is still hope since the robots are currently inside the
school, and it is not known if they can get out. Your task is, given the floor
plan of the school and the locations of the robots, determine if any of them
can escape, or if they're all stuck inside.

The floor plan is given as an $n\times m$ matrix consisting of the following characters:

\begin{itemize}
    \item `\texttt{.}' denoting empty floor space
    \item `\texttt{\#}' denoting a wall or a closed door
    \item `\texttt{X}' denoting a robot
\end{itemize}

Robots can drive to adjacent empty floor spaces (but not diagonally).

A robot can escape outside if it can reach the edge of the floor plan.

\section*{Input}
The first line of input contains two integers $n, m$ ($ 1 \leq n,m \leq 1000$),
the dimensions of the floor plan. Then
follow $n$ lines, each containing $m$ characters, describing the floor plan as
defined above. You can assume that no robots or walls are on the border of the
floor plan.

\section*{Output}
Output one line containing ``\texttt{Death to humans}'' if any of the robots
can escape, or ``\texttt{We are safe}'' otherwise.

\section*{Points}
Your solution will be tested on several test case groups.
To get the points for a group, it must pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $63$      & $1 \le n, m \le 100$ \\ \hline
  $2$    & $37$      & No additional constraints. \\ \hline
\end{tabular}

